A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers

### 2019-02-14 Thesis/Appendices/Lambert.tex
Edited appendices
Minor edits

\chapter{The Lambert $W$ Function}
\label{chap:lambertw}
The Lambert $W$ function is defined to be the inverse of the function $f(x) = x \textrm{e}^x$ and its graph is shown in Figure \ref{fig:lambertw}. In other words, if $z = x \textrm{e}^x$ then $x = W(z)$. Notice that by combining these relations we obtain the identities
\begin{align}
\label{eq:lambertw}
z &= W(z) \textrm{e}^{W(z)}, & x &= W(x \textrm{e}^x).
\end{align}
This function is called the Lambert $W$ function because it is the logarithm of a special instance of Lambert's series---the letter $W$ is used because of the work done by E. M. Wright \cite{lambertw}.

Notice that the original function, $f(x) = x \textrm{e}^x$, is \emph{not} injective, and as a consequence, the $W$ function is multi-valued on the interval $[-1/\textrm{e},0)$. To alleviate this, occasionally the branch $W(x) \geq -1$ is denoted $W_0$ and is called the principal or upper branch, whereas the branch $W(x) < -1$ is denoted $W_{-1}$ and is called the lower branch. However, in this work the $W$ function will only take positive real values and so this distinction is not needed.

@@

The Lambert $W$ function has applications in various areas of math and physics \cite{lambertw} including:
\begin{itemize}
\item Jet fuel problems
\item Combustion problems
\item Enzyme kinetics problems
\item Linear constant coefficient differential delay equations
\item Volterra equations.
\end{itemize}
Primarily, the $W$ function arises when solving iterated exponentiation or certain algebraic equations. For example, consider the equation $z = x^x$. By taking the logarithm of each side we have
\begin{align*}
\log z &= x \log x, \\
&= \log x \textrm{e}^{\log x},
\end{align*}
which after applying the $W$ function reduces to $W(\log z) = \log x$ by \eqref{eq:lambertw}. Finally, $x$ as a function of $z$ can be written as $x = \exp(W(\log z))$.

>>>>

\chapter{The Lambert $W$ Function}
\label{chap:lambertw}
The Lambert $W$ function is defined to be the inverse of the function $f(x) = x \textrm{e}^x$; its graph is shown in Figure \ref{fig:lambertw}. In other words, if $z = x \textrm{e}^x$ then $x = W(z)$. Notice that by combining these relations we obtain the identities
\begin{align}
\label{eq:lambertw}
z &= W(z) \textrm{e}^{W(z)}, & x &= W(x \textrm{e}^x).
\end{align}
This function is called the Lambert $W$ function because it is the logarithm of a special instance of Lambert's series---the letter $W$ is used because of the work done by E. M. Wright \cite{corless}. \\

Notice that the original function, $f(x) = x \textrm{e}^x$, is \emph{not} injective, and as a consequence, the $W$ function is multi-valued on the interval $[-1/\textrm{e},0)$. To alleviate this, occasionally the branch $W(x) \geq -1$ is denoted $W_0$ and is called the principal or upper branch, whereas the branch $W(x) < -1$ is denoted $W_{-1}$ and is called the lower branch. However, in this work the $W$ function will only take positive real values and so this distinction is not needed. \\

@@

The Lambert $W$ function has applications in various areas of math and physics \cite{corless} including:
\begin{itemize}
\item Jet fuel problems
\item Combustion problems
\item Enzyme kinetics problems
\item Linear constant coefficient differential delay equations
\item Volterra equations.
\end{itemize}
Primarily, the $W$ function arises when solving iterated exponentiation or certain algebraic equations. For example, consider the equation $z = x^x$. By taking the logarithm of each side we have
\begin{align*}
\log z &= x \log x, \\
&= \log x \textrm{e}^{\log x},
\end{align*}
which after applying the $W$ function reduces to $W(\log z) = \log x$ by \eqref{eq:lambertw}. Finally, $x$ as a function of $z$ can be written as $x = \exp(W(\log z))$.

### 2019-02-14 Thesis/Figures/Cavity.tex
Added/updated figures
Minor edits

\begin{tikzpicture}
% Two laser loops
\draw [rounded corners=4mm] (0,0) rectangle ++(9,4);
\draw [rounded corners=4mm] (0,0) rectangle ++(-1,4);

% Gain
\draw (0.5,2.25) circle (0.5cm);
\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er Doped \\ Fibre};
\draw (0.5,1.75) circle (0.5cm);

% Modulator and pump
\filldraw[fill=white, draw=black] (3.5,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
\filldraw[fill=white, draw=black] (-1.6,1.5) rectangle ++(1.2,1) node [midway] {Pump};

% Coupler and output
\draw[-{Latex[length=2.5mm]}] (4.5,4) -- (4.5,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
\draw[densely dashdotted] (4,3.5) -- (5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ Coupler};

% Circulator
\filldraw[fill=white, draw=black] (9,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Optical \\ Circulator};
\draw (9,2.5) arc (0:-90:0.5cm);
\draw (9,1.5) arc (0:90:0.5cm);

@@

% Arrows
\draw[-{Latex[length=2.5mm]}] (2.16,0) -- (2.15,0);
\draw[-{Latex[length=2.5mm]}] (2.39,4) -- (2.4,4);
\draw[-{Latex[length=2.5mm]}] (6.76,0) -- (6.75,0);
\draw[-{Latex[length=2.5mm]}] (7.09,4) -- (7.1,4);
\draw[-{Latex[length=2.5mm]}] (-0.649,0) -- (-0.65,0);
\draw[-{Latex[length=2.5mm]}] (-0.351,4) -- (-0.35,4);
\draw[-{Latex[length=2.5mm]}] (8.807,2.11) -- (8.8,2.1);
\draw[-{Latex[length=2.5mm]}] (8.96,1.712) -- (8.97,1.7);
\end{tikzpicture}

>>>>

% !TeX root = ../Thesis.tex

\begin{tikzpicture}
% Two laser loops
\draw [rounded corners=4mm] (0,0) rectangle ++(9,4);
\draw [rounded corners=4mm] (0,0) rectangle ++(-1.5,4);

% Gain
\draw (0.5,2.25) circle (0.5cm);
\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-Doped \\ Fibre};
\draw (0.5,1.75) circle (0.5cm);

% Modulator and pump
\filldraw[fill=white, draw=black] (3.5,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
\filldraw[fill=white, draw=black] (-2.1,1.5) rectangle ++(1.2,1) node [midway] {Pump};

% Coupler and output
\draw[-stealth] (4.5,4) -- (4.5,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
\draw[densely dashdotted] (4,3.5) -- (5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ Coupler};

% Circulators
\filldraw[fill=white, draw=black] (9,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Optical \\ Circulator};
\draw[->,>=stealth] (9,2.325) arc (90:360:0.325cm);

\filldraw[fill=white, draw=black] (0,0) circle (0.5cm);
\draw[->,>=stealth] (0,0.325) arc (90:360:0.325cm);

\filldraw[fill=white, draw=black] (0,4) circle (0.5cm);
\draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);

@@

% Arrows
%\draw[-stealth] (2.16,0) -- (2.15,0);
%\draw[-stealth] (2.39,4) -- (2.4,4);
%\draw[-stealth] (6.76,0) -- (6.75,0);
%\draw[-stealth] (7.09,4) -- (7.1,4);
%\draw[-stealth] (-0.649,0) -- (-0.65,0);
%\draw[-stealth] (-0.351,4) -- (-0.35,4);
\end{tikzpicture}
